### 2015-12-14 paper/main.tex
update versions

We compare results of \ashr with existing FDR-based methods implemented
in the R packages \qvalue (v2.0 from Bioconductor), \locfdr (v1.1-7 from \url{https://cran.r-project.org/src/contrib/Archive/locfdr/}), and \mixfdr (v1.0, from \url{https://cran.r-project.org/src/contrib/Archive/mixfdr/}).  In all our simulations we assume that the test statistics follow the expected theoretical distribution under the null, and we indicate this
to \locfdr using {\tt nulltype=0} and to \mixfdr using {\tt theonull=TRUE}. Otherwise all packages were used with default options.

>>>>

We compare results of \ashr with existing FDR-based methods implemented
in the R packages \qvalue (v2.1.1), \locfdr (v1.1-8), and \mixfdr (v1.0, from \url{https://cran.r-project.org/src/contrib/Archive/mixfdr/}).  
In all our simulations we assume that the test statistics follow the expected theoretical distribution under the null, and we indicate this
to \locfdr using {\tt nulltype=0} and to \mixfdr using {\tt theonull=TRUE}. Otherwise all packages were used with default options.
